\Large Inferential Analysis of the Supreme Court Citation Network

### 2018-04-12 Tex/paper.tex

@@

\begin{itemize}
\item ToDo: mention new variable: overruled cases
\end{itemize}

@@

>>>>

\begin{itemize}
\item add to the discussion to which degree network statistics reflect causual relation
\end{itemize}

@@

\begin{itemize}
\item mention new variable: overruled cases
\item mention new variable: nodemix(same issue area)
\item mention new variable:Sender/receiver effect for judge who wrote majority opinion
\item Same justice homophily with time trend
\item Argue/justify why certain covariates are included
\end{itemize}

@@

\begin{itemize}
\item visualize Sender/receiver Issue Area Results
\item heatplot for issue area nodemix
\item visualize Sender/receiver for majority opinion writer
\item add Network effect plots for model without network statistics (add to existing plots?)
\end{itemize}

\section{Appendix}
The following table presents the Bootstrapped MPLE Results for the time period $1937-2015$.

\begin{itemize}
\item add robustness check: MCMLE for each year -> plot time trend of coefs -> are results similar to the MPLE time trends presented in the paper?
\item (investigate which statistic contributes most on recall improvement)
\end{itemize}
